Grounding the interaction: anchoring situated discourse in everyday human-robot interaction

### 2011-07-15 paper_knowledge.tex
Fixed some issues with biblio + added Sisbot2011 on SPARK

Anchoring perceptions in a symbolic model requires first perception abilities
and second, a symbolic assessment of the percepts. In this section we present
SPARK (\emph{SPAtial Reasoning \& Knowledge}), a situation assessment reasoner
that generates relevant symbolic information from the geometry of the
environment with respect to relations between objects and human capabilities.
Moreover, the notion of \emph{Perspective
Taking}~\cite{Flavell1992,Tversky1999} is employed in the heart of the
reasoning to provide the robot with the ability to put itself at the human's
place and to reason about the world from different perspectives.

>>>>

Anchoring perceptions in a symbolic model requires first perception abilities
and second, a symbolic assessment of the percepts. In this section we present
SPARK (\emph{SPAtial Reasoning \& Knowledge}, \cite{Sisbot2011}), a situation assessment reasoner
that generates relevant symbolic information from the geometry of the
environment with respect to relations between objects and human capabilities.
Moreover, the notion of \emph{Perspective
Taking}~\cite{Flavell1992,Tversky1999} is employed in the heart of the
reasoning to provide the robot with the ability to put itself at the human's
place and to reason about the world from different perspectives.
